### 2023-02-02 definitions.tex
up

\begin{proposition}\cite{DBLP:journals/tcs/FinkelS01}
If $S$ is a WSTS with strong monotony and $I \subseteq S$ is an upward-closed set of states, then $\pred(I )$ is upward-closed.
\end{proposition}
\alain{étrange ces deux propositions, l'une suffirait}
\iffalse
Proof. Assume $s \in \pred (I )$. Then $s \rightarrow t$ for some $t \in I $. If now $s' \geq s$ then strong upward-compatibility entails that $s' \rightarrow t'$ for some $t' \geq t$. Then $t' \in I$ and $s' \in \pred(I )$.
\fi

@@

A downard-closed set $J$ is {\em decidable} if, given $s \in S$, it is decidable whether
$s \in J$. 
Since a downward-closed set does not have an ``upward-basis'' in general, we will demand that membership is decidable.
\alain{remarque pas claire}
% \textcolor{red}{Do we still demand this ?}

@@

\begin{fact}\label{fact basis}
% Fact 3 ([1]). 
% Parosh Aziz Abdulla, Karlis Cerans, Bengt Jonsson & Yih-Kuen Tsay (1996): General Decidability Theorems for Infinite-State Systems. In: Proc. LICS 1996, IEEE Computer Society Press, pp. 313–321,

(i) For every upward-closed set $I \subseteq S$, there exists a finite basis $B$ of $I$.

(ii) Given a finite set $A \subseteq S$ with $I =\uparrow A$, we can compute a finite basis $B$ of $I$.
\alain{(ii) est bizarre car A est déjà une base finie de $\uparrow A$, et $min(A)$ est la base minimale}

\end{fact}

>>>>

\begin{proposition}\cite{DBLP:journals/tcs/FinkelS01}
If $S$ is a WSTS with strong monotony and $I \subseteq S$ is an upward-closed set of states, then $\pred(I )$ is upward-closed.
\end{proposition}
\alain{étrange ces deux propositions, l'une suffirait}
\iffalse
Proof. Assume $s \in \pred (I )$. Then $s \rightarrow t$ for some $t \in I $. If now $s' \geq s$ then strong upward-compatibility entails that $s' \rightarrow t'$ for some $t' \geq t$. Then $t' \in I$ and $s' \in \pred(I )$.
\fi
\mathieu{On peut probablement enlever la Proposition $8$ alors. La proposition $9$ étant plus directement pertinente pour les lemmes/preuves (permet d'avoir itérativement $\pred^k(I)$ upward-closed if $I$ upward-closed - for all $k$).}

@@

A downard-closed set $J$ is {\em decidable} if, given $s \in S$, it is decidable whether
$s \in J$. 
\textcolor{red}{Since a downward-closed set does not have an ``upward-basis'' in general, we will demand that membership is decidable.}
\alain{remarque pas claire}
% \textcolor{red}{Do we still demand this ?}
\mathieu{On peut enlever ce point de discussion ici et en discuter de manière plus complête au moment où on discute de SAFE et BAD plus en détail je pense.}

@@

\begin{fact}\label{fact basis}
% Fact 3 ([1]). 
% Parosh Aziz Abdulla, Karlis Cerans, Bengt Jonsson & Yih-Kuen Tsay (1996): General Decidability Theorems for Infinite-State Systems. In: Proc. LICS 1996, IEEE Computer Society Press, pp. 313–321,
For every upward-closed set $I \subseteq S$, there exists a finite basis $B$ of $I$. 
% (ii) Given a finite set $A \subseteq S$ with $I =\uparrow A$, we can compute a finite basis $B$ of $I$.
% \alain{(ii) est bizarre car A est déjà une base finie de $\uparrow A$, et $min(A)$ est la base minimale}
\end{fact}
